---
title: "FC_Heatmap_Example"
author: "Pete Millar & Nawang Singhe"
date: '2022-07-18'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Clear workspace
```{r}
rm(list=ls())
```
#load packages
```{r}
pacman::p_load(mclust,MineICA,sBIC, jtools, psych, cowplot, multcomp, ggplot2, patchwork, data.table, readxl, DescTools, lattice, tidyverse, boot, table1, ggpubr, effects, kableExtra, magick, webshot, install = TRUE)
```

###FC Matrix
```{r, echo = FALSE, message = FALSE, warning = FALSE}

#load network level FC matrix
##This one has been pregenerated, but the goal would be for you to create a new one
##consisting of t values of the parameters of interest (amyloid, tau, amyloid*tau)
##from the regression models of interest (3, 4, and 5. you can forget model 1)
rs_fcmat = read.csv("fcmat_254.csv", row.names = 1)

#library(lattice) #package for levelplot() function
##define colormap (these can be tweaked to optimize presentation)
bcyor = colorRampPalette(c("blue","cyan", "yellow", "orange", "red"))(256)
bcyr = colorRampPalette(c("blue","cyan", "yellow", "red"))(256)
bwr = colorRampPalette(c("blue", "white", "red"))(256)
#rs_fcmatrix = as.matrix(rs_fcmat[,2:14])
#rownames(rs_fcmatrix) = 
ry = colorRampPalette(c("red", "yellow"))(256)
#png("rs_fcmat_254_bwr.png", height = 400, width = 400)
#png("rs_fcmat_254_bcyor.png", height = 400, width = 400)
png("rs_fcmat_254_bcyr.png", height = 400, width = 400) #used to save file to png output

levelplot(t(as.matrix(rs_fcmat[c(nrow(rs_fcmat):1), ])), 
          #col.regions = bwr, at = seq(-.6, .6, .01), 
          #col.regions = bcyor, at = seq(-.2, .6, .01),
          col.regions = bcyr, at = seq(-.3, .7, .01), 
          scale=list(x=list(rot=90))
          , xlab = "", ylab = ""
          )
dev.off() #end function to save output to png

```

#define data frames and variables
```{r}
#df with necessary variables
hm_data <- data
maxNeg = min(hm_data$Centiloid_merge)
hm_data <- hm_data %>%
  mutate(age_tau=abs(as.Date(BIRTH,format = "%m/%d/%Y")-as.Date(date_tau,format = "%m/%d/%Y"))/365.25) %>%
  mutate(logCentiloidplus = log(Centiloid_merge - maxNeg + 3)) %>%
  mutate(logTau = log(Tauopathy)) -> hm_data

hm_data$centCategory <- cut(hm_data$Centiloid_merge, breaks = c(-Inf, 20.6, +Inf), labels = c("Cent-", "Cent+"))
table(hm_data$centCategory)

hm_data$at_int = hm_data$Centiloid_merge * hm_data$Tauopathy
hm_data$logat_int = hm_data$logCentiloidplus * hm_data$logTau

hm_final = hm_data %>% dplyr::select(MAPID,
                                     mean_FD_pre_threshold, GENDER, EDUC, age_tau, #covariates
                                     NA_x_NA:CEREB_x_CEREB, #networks
                                     Centiloid_merge, Tauopathy, #raw values
                                     logCentiloidplus, logTau, #log values
                                     centCategory, #binarization
                                     at_int, logat_int) #for reproducing Schultz fig. 1
#create a list of dependent variables
df_networks <- hm_final %>%
  ungroup() %>%
  dplyr::select(NA_x_NA:CEREB_x_CEREB)
dep.vars <- colnames(df_networks)

#create function for heatmaps
empty_matrix <- data.frame(matrix(ncol = 14, nrow = 14))
dim <- c('na', 'sm', 'sm_lat', 'co', 'aud', 'dmn', 'mem',
         'vis', 'fp', 'sal', 'SUBCort', 'van', 'dan', 'cereb')

```

#create functions
```{r}

### initialize matrix ###
make_hm <- function() {
  new_matrix <- empty_matrix
  colnames(new_matrix) <- dim
  row.names(new_matrix) <- dim
  return( new_matrix)
}

### convert summary to table ###
convert_tbl <- function(tbl) {
  tidy_tbl <- tidy(tbl)
  tbl <- as.data.frame(tidy_tbl)
  return(tbl)
}
```

#LOG petmr data analyis
```{r}
### run models for log values ###
run_log_petmr1 <- function(dep.var) {
    fml <- reformulate(c("logCentiloidplus", "age_tau", "EDUC", "GENDER", "mean_FD_pre_threshold"), dep.var)
    lm(fml, data=hm_final)
}

run_log_petmr2 <- function(dep.var) {
    fml <- reformulate(c("logTau", "age_tau", "EDUC", "GENDER", "mean_FD_pre_threshold"), dep.var)
    lm(fml, data=hm_final)
}

run_log_petmr3 <- function(dep.var) {
    fml <- reformulate(c("logCentiloidplus", "logTau", "age_tau", "EDUC", "GENDER", "mean_FD_pre_threshold"), dep.var)
    lm(fml, data=hm_final)
}

run_log_petmr4 <- function(dep.var) {
    fml <- reformulate(c("logCentiloidplus*logTau", "logCentiloidplus", "logTau", "age_tau", "EDUC", "GENDER", "mean_FD_pre_threshold"), dep.var)
    lm(fml, data=hm_final)
}

run_log_petmr5 <- function(dep.var) {
    fml <- reformulate(c("centCategory*logTau", "centCategory", "logTau", "age_tau", "EDUC", "GENDER", "mean_FD_pre_threshold"), dep.var)
    lm(fml, data=hm_final)
}

#run functions
petmr_log1 <- sapply(dep.vars, run_log_petmr1, simplify = FALSE)
pl1_summaries <- lapply(petmr_log1, summary)

petmr_log2 <- sapply(dep.vars, run_log_petmr2, simplify = FALSE)
pl2_summaries <- lapply(petmr_log2, summary)

petmr_log3 <- sapply(dep.vars, run_log_petmr3, simplify = FALSE)
pl3_summaries <- lapply(petmr_log3, summary)

petmr_log4 <- sapply(dep.vars, run_log_petmr4, simplify = FALSE)
pl4_summaries <- lapply(petmr_log4, summary)

petmr_log5 <- sapply(dep.vars, run_log_petmr5, simplify = FALSE)
pl5_summaries <- lapply(petmr_log5, summary)


```

#LOGPETMR LARGE TABLE
```{r}
petmr_log_stat_table <- data.frame(matrix(ncol = 210, nrow = 6))
colnames(petmr_log_stat_table)[seq(1,ncol(petmr_log_stat_table),1)] <- c("t-stat","p-val")

num_networks = 105
# #model 1: centiloid
for (i in 1:num_networks) {
  index = i * 2
  lm <- convert_tbl(petmr_log1[[i]])
  t_val <- lm[2,4]
  petmr_log_stat_table[1,index-1] = t_val
  p_val <- lm[2,5]
  petmr_log_stat_table[1,index] = p_val
    }
# #model 2: tau
for (i in 1:num_networks) {
  index = i * 2
  lm <- convert_tbl(petmr_log2[[i]])
  t_val <- lm[2,4]
  petmr_log_stat_table[2,index-1] = t_val
  p_val <- lm[2,5]
  petmr_log_stat_table[2,index] = p_val
    }

#model 3: centiloid and tau
for (i in 1:num_networks) {
  index = i * 2
  lm <- convert_tbl(petmr_log3[[i]])
  t_val_cent <- lm[2,4]
  petmr_log_stat_table[3,index-1] = t_val_cent
  t_val_tau <- lm[3,4]
  petmr_log_stat_table[4,index-1] = t_val_tau
  
  p_val_cent <- lm[2,5]
  petmr_log_stat_table[3,index] = p_val_cent
  p_val_tau <- lm[3,5]
  petmr_log_stat_table[4,index] = p_val_tau
    }
#model 4: continuous interaction
for (i in 1:num_networks) {
  index = i * 2
  lm <- convert_tbl(petmr_log4[[i]])
  t_val <- lm[8,4]
  petmr_log_stat_table[5,index-1] = t_val
  p_val <- lm[8,5]
  petmr_log_stat_table[5,index] = p_val
    }
#model 5: binarized interaction
for (i in 1:num_networks) {
  index = i * 2
  lm <- convert_tbl(petmr_log5[[i]])
  t_val <- lm[8,4]
  petmr_log_stat_table[6,index-1] = t_val
  p_val <- lm[8,5]
  petmr_log_stat_table[6,index] = p_val
    }
```

#t-value matrices

```{r}
petmr_tval1l <- make_hm() #log data
petmr_tval2l <- make_hm()
petmr_tval3lcent <- make_hm()
petmr_tval3ltau <- make_hm()
petmr_tval4l <- make_hm()
petmr_tval5l <- make_hm()


### extract centiloid t-statistics from raw models ###
## model 1 ##
# log data #
for (i in 1:nrow(empty_matrix)) {
  index = -i^2 + 31*i - 29
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      t_val <- petmr_log_stat_table[1,index]
      petmr_tval1l[i,j] = t_val
   }
    if (i < j) {
      update_index = index - 2*i + 2*j
      t_val <- petmr_log_stat_table[1,update_index]
      petmr_tval1l[i,j] = t_val
      petmr_tval1l[j,i] = petmr_tval1l[i,j]
    }
  }
}

## model 2 ##
# log #
for (i in 1:nrow(empty_matrix)) {
  index = -i^2 + 31*i - 29
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      t_val <- petmr_log_stat_table[2,index]
      petmr_tval2l[i,j] = t_val
   }
    if (i < j) {
      update_index = index - 2*i + 2*j
      t_val <- petmr_log_stat_table[2,update_index]
      petmr_tval2l[i,j] = t_val
      petmr_tval2l[j,i] = petmr_tval2l[i,j]
    }
  }
}

## model3 ##
# log centiloid #
for (i in 1:nrow(empty_matrix)) {
  index = -i^2 + 31*i - 29
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      t_val <- petmr_log_stat_table[3,index]
      petmr_tval3lcent[i,j] = t_val
   }
    if (i < j) {
      update_index = index - 2*i + 2*j
      t_val <- petmr_log_stat_table[3,update_index]
      petmr_tval3lcent[i,j] = t_val
      petmr_tval3lcent[j,i] = petmr_tval3lcent[i,j]
    }
  }
}
# log tau #
for (i in 1:nrow(empty_matrix)) {
  index = -i^2 + 31*i - 29
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      t_val <- petmr_log_stat_table[4,index]
      petmr_tval3ltau[i,j] = t_val
   }
    if (i < j) {
      update_index = index - 2*i + 2*j
      t_val <- petmr_log_stat_table[4,update_index]
      petmr_tval3ltau[i,j] = t_val
      petmr_tval3ltau[j,i] = petmr_tval3ltau[i,j]
    }
  }
}

## model 4 ##
# log A x T interaction #
for (i in 1:nrow(empty_matrix)) {
  index = -i^2 + 31*i - 29
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      t_val <- petmr_log_stat_table[5,index]
      petmr_tval4l[i,j] = t_val
   }
    if (i < j) {
      update_index = index - 2*i + 2*j
      t_val <- petmr_log_stat_table[5,update_index]
      petmr_tval4l[i,j] = t_val
      petmr_tval4l[j,i] = petmr_tval4l[i,j]
    }
  }
}

## model 5 - binarized interaction effect ##
# log data #
for (i in 1:nrow(empty_matrix)) {
  index = -i^2 + 31*i - 29
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      t_val <- petmr_log_stat_table[6,index]
      petmr_tval5l[i,j] = t_val
   }
    if (i < j) {
      update_index = index - 2*i + 2*j
      t_val <- petmr_log_stat_table[6,update_index]
      petmr_tval5l[i,j] = t_val
      petmr_tval5l[j,i] = petmr_tval5l[i,j]
    }
  }
}

```

#p-value matrices

```{r}

### p-values ###

petmr_pval3lcent <- make_hm()
petmr_pval3ltau <- make_hm()
petmr_pval4l <- make_hm()
petmr_pval5l <- make_hm()

### model 3 log ###
# log centiloid #
for (i in 1:nrow(empty_matrix)) {
  index = -i^2 + 31*i - 29
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      t_val <- petmr_log_stat_table[3,index+1]
      petmr_pval3lcent[i,j] = t_val
   }
    if (i < j) {
      update_index = index + 1 - 2*i + 2*j
      t_val <- petmr_log_stat_table[3,update_index]
      petmr_pval3lcent[i,j] = t_val
      petmr_pval3lcent[j,i] = petmr_pval3lcent[i,j]
    }
  }
}

# log tau #
for (i in 1:nrow(empty_matrix)) {
  index = -i^2 + 31*i - 29
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      t_val <- petmr_log_stat_table[4,index+1]
      petmr_pval3ltau[i,j] = t_val
   }
    if (i < j) {
      update_index = index + 1 - 2*i + 2*j
      t_val <- petmr_log_stat_table[4,update_index]
      petmr_pval3ltau[i,j] = t_val
      petmr_pval3ltau[j,i] = petmr_pval3ltau[i,j]
    }
  }
}

### model 4 ###
# log A x T interaction #
for (i in 1:nrow(empty_matrix)) {
  index = -i^2 + 31*i - 29
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      t_val <- petmr_log_stat_table[5,index+1]
      petmr_pval4l[i,j] = t_val
   }
    if (i < j) {
      update_index = index + 1 - 2*i + 2*j
      t_val <- petmr_log_stat_table[5,update_index]
      petmr_pval4l[i,j] = t_val
      petmr_pval4l[j,i] = petmr_pval4l[i,j]
    }
  }
}

### model 5 ###
# log A x T binarized #
for (i in 1:nrow(empty_matrix)) {
  index = -i^2 + 31*i - 29
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      t_val <- petmr_log_stat_table[6,index+1]
      petmr_pval5l[i,j] = t_val
   }
    if (i < j) {
      update_index = index + 1 - 2*i + 2*j
      t_val <- petmr_log_stat_table[6,update_index]
      petmr_pval5l[i,j] = t_val
      petmr_pval5l[j,i] = petmr_pval5l[i,j]
    }
  }
}
```



#FDR corrected p value matrices
```{r}
#model 3 amyloid
cpet_3lcent <- petmr_pval3lcent
for (i in  1:nrow(empty_matrix)){
  for (j in 1: nrow(empty_matrix)) {
    if (i > j) {
      cpet_3lcent[i,j] = 10
      }
    }
  }
cpet_3lcent <- cpet_3lcent %>%
  matrix() %>%
  unlist()
cpet_3lcent <- cpet_3lcent[ order(cpet_3lcent) ]
cpet_3lcent <- cpet_3lcent[! (cpet_3lcent >= 1)]

p.adjust(cpet_3lcent, method = "fdr", )

# model 3 tau
cpet_3ltau <- petmr_pval3ltau
for (i in  1:nrow(empty_matrix)){
  for (j in 1: nrow(empty_matrix)) {
    if (i > j) {
      cpet_3ltau[i,j] = 10
      }
    }
  }
cpet_3ltau <- cpet_3ltau %>%
  matrix() %>%
  unlist()
cpet_3ltau <- cpet_3ltau[ order(cpet_3ltau) ]
cpet_3ltau <- cpet_3ltau[! (cpet_3ltau >= 1)]

p.adjust(cpet_3ltau, method = "fdr", )

#model 4 continuous
cpet_4l <- petmr_pval4l
for (i in  1:nrow(empty_matrix)){
  for (j in 1: nrow(empty_matrix)) {
    if (i > j) {
      cpet_4l[i,j] = 10
      }
    }
  }
cpet_4l <- cpet_4l %>%
  matrix() %>%
  unlist()
cpet_4l <- cpet_4l[ order(cpet_4l) ]
cpet_4l <- cpet_4l[! (cpet_4l >= 1)]

p.adjust(cpet_4l, method = "fdr", )

#model 5 binarized
cpet_5l <- petmr_pval5l
for (i in  1:nrow(empty_matrix)){
  for (j in 1: nrow(empty_matrix)) {
    if (i > j) {
      cpet_5l[i,j] = 10
      }
    }
  }
cpet_5l <- cpet_5l %>%
  matrix() %>%
  unlist()
cpet_5l <- cpet_5l[ order(cpet_5l) ]
cpet_5l <- cpet_5l[! (cpet_5l >= 1)]

p.adjust(cpet_5l, method = "fdr", )
 

```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
