---
title: "FC_Heatmap_Example"
author: "Pete Millar & Nawang Singhe"
date: '2022-07-18'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Clear workspace
```{r}
rm(list=ls())
```
#load packages
```{r}
pacman::p_load(mclust,MineICA,sBIC, jtools, psych, cowplot, multcomp, ggplot2, patchwork, data.table, readxl, DescTools, lattice, tidyverse, boot, table1, ggpubr, effects, kableExtra, magick, webshot, install = TRUE)
```

###FC Matrix
```{r, echo = FALSE, message = FALSE, warning = FALSE}

#load network level FC matrix
##This one has been pregenerated, but the goal would be for you to create a new one
##consisting of t values of the parameters of interest (amyloid, tau, amyloid*tau)
##from the regression models of interest (3, 4, and 5. you can forget model 1)
rs_fcmat = read.csv("fcmat_254.csv", row.names = 1)

#library(lattice) #package for levelplot() function
##define colormap (these can be tweaked to optimize presentation)
bcyor = colorRampPalette(c("blue","cyan", "yellow", "orange", "red"))(256)
bcyr = colorRampPalette(c("blue","cyan", "yellow", "red"))(256)
bwr = colorRampPalette(c("blue", "white", "red"))(256)
#rs_fcmatrix = as.matrix(rs_fcmat[,2:14])
#rownames(rs_fcmatrix) = 

#png("rs_fcmat_254_bwr.png", height = 400, width = 400)
#png("rs_fcmat_254_bcyor.png", height = 400, width = 400)
png("rs_fcmat_254_bcyr.png", height = 400, width = 400) #used to save file to png output

levelplot(t(as.matrix(rs_fcmat[c(nrow(rs_fcmat):1), ])), 
          #col.regions = bwr, at = seq(-.6, .6, .01), 
          #col.regions = bcyor, at = seq(-.2, .6, .01),
          col.regions = bcyr, at = seq(-.3, .7, .01), 
          scale=list(x=list(rot=90))
          , xlab = "", ylab = ""
          )
dev.off() #end function to save output to png

```

#define data frames and variables
```{r}
#df with necessary variables
hm_data <- data
maxNeg = min(hm_data$Centiloid_merge)
hm_data <- hm_data %>%
  mutate(age_tau=abs(as.Date(BIRTH,format = "%m/%d/%Y")-as.Date(date_tau,format = "%m/%d/%Y"))/365.25) %>%
  mutate(logCentiloidplus = log(Centiloid_merge - maxNeg + 3)) %>%
  mutate(logTau = log(Tauopathy)) -> hm_data

hm_data$centCategory <- cut(hm_data$Centiloid_merge, breaks = c(-Inf, 20.6, +Inf), labels = c("Cent-", "Cent+"))
table(hm_data$centCategory)

hm_data$at_int = hm_data$Centiloid_merge * hm_data$Tauopathy
hm_data$logat_int = hm_data$logCentiloidplus * hm_data$logTau

hm_final = hm_data %>% dplyr::select(MAPID,
                                     mean_FD_pre_threshold, GENDER, EDUC, age_tau, #covariates
                                     NA_x_NA:CEREB_x_CEREB, #networks
                                     Centiloid_merge, Tauopathy, #raw values
                                     logCentiloidplus, logTau, #log values
                                     centCategory, #binarization
                                     at_int, logat_int) #for reproducing Schultz fig. 1
#create a list of dependent variables
df_networks <- hm_final %>%
  ungroup() %>%
  dplyr::select(NA_x_NA:CEREB_x_CEREB)
dep.vars <- colnames(df_networks)

#create function for heatmaps
empty_matrix <- data.frame(matrix(ncol = 14, nrow = 14))
dim <- c('na', 'sm', 'sm_lat', 'co', 'aud', 'dmn', 'mem',
         'vis', 'fp', 'sal', 'SUBCort', 'van', 'dan', 'cereb')

```

#define functions
```{r}
### initialize matrix ###
make_hm <- function() {
  new_matrix <- empty_matrix
  colnames(new_matrix) <- dim
  row.names(new_matrix) <- dim
  return( new_matrix)
}

### run models for raw values ###
run_model3 <- function(dep.var) {
    fml <- reformulate(c("Centiloid_merge", "Tauopathy", "age_tau", "EDUC", "GENDER", "mean_FD_pre_threshold"), dep.var)
    lm(fml, data=hm_final)
}

run_model4 <- function(dep.var) {
    fml <- reformulate(c("Centiloid_merge*Tauopathy", "Centiloid_merge", "Tauopathy", "age_tau", "EDUC", "GENDER", "mean_FD_pre_threshold"), dep.var)
    lm(fml, data=hm_final)
}

run_model5 <- function(dep.var) {
    fml <- reformulate(c("centCategory*Tauopathy", "centCategory", "Tauopathy", "age_tau", "EDUC", "GENDER", "mean_FD_pre_threshold"), dep.var)
    lm(fml, data=hm_final)
}

### run models for log values ###
run_logmodel3 <- function(dep.var) {
    fml <- reformulate(c("logCentiloidplus", "logTau", "age_tau", "EDUC", "GENDER", "mean_FD_pre_threshold"), dep.var)
    lm(fml, data=hm_final)
}

run_logmodel4 <- function(dep.var) {
    fml <- reformulate(c("logCentiloidplus*logTau", "logCentiloidplus", "logTau", "age_tau", "EDUC", "GENDER", "mean_FD_pre_threshold"), dep.var)
    lm(fml, data=hm_final)
}

run_logmodel5 <- function(dep.var) {
    fml <- reformulate(c("centCategory*logTau", "centCategory", "logTau", "age_tau", "EDUC", "GENDER", "mean_FD_pre_threshold"), dep.var)
    lm(fml, data=hm_final)
}

### convert summary to table ###
convert_tbl <- function(tbl) {
  tidy_tbl <- tidy(tbl)
  tbl <- as.data.frame(tidy_tbl)
  return(tbl)
}
```


#model 3: heatmap of centiloid and tau (main effects only)
```{r}
# LM SUMMARIES #

### raw values ###
raw_model3 <- sapply(dep.vars, run_model3, simplify = FALSE)
rm3_summaries <- lapply(raw_model3, summary)
rm3_summaries$NA_x_NA #sanity check

### log values ###
log_model3 <- sapply(dep.vars, run_logmodel3, simplify = FALSE)
lm3_summaries <- lapply(log_model3, summary)
lm3_summaries$NA_x_NA #sanity check

# POPULATE HEATMAP MATRICES #
hm_raw_m3 <- make_hm()
hm_log_m3 <- make_hm()

hm_raw_m3_tau <- make_hm()
hm_log_m3_tau <- make_hm()

### extract centiloid t-statistics from raw models ###
for (i in 1:nrow(empty_matrix)) {
  index = 0.5 * (-i^2 + 31*i - 28)
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      lm <- convert_tbl(raw_model3[[index]])
      t_val <- lm[2,4]
      hm_raw_m3[i, j] = t_val
   }
    if (i < j) {
      update_index = index + j - i
      hm_raw_m3[i,j] = update_index
      lm <- convert_tbl(raw_model3[[update_index]])
      t_val <- lm[2,4]
      hm_raw_m3[i,j] = t_val
      hm_raw_m3[j,i] = hm_raw_m3[i,j]
    }
  }
}

### extract centiloid t-statistics from log models ###
for (i in 1:nrow(empty_matrix)) {
  index = 0.5 * (-i^2 + 31*i - 28)
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      lm <- convert_tbl(log_model3[[index]])
      t_val <- lm[2,4]
      hm_log_m3[i, j] = t_val
   }
    if (i < j) {
      update_index = index + j - i
      hm_log_m3[i,j] = update_index
      lm <- convert_tbl(log_model3[[update_index]])
      t_val <- lm[2,4]
      hm_log_m3[i,j] = t_val
      hm_log_m3[j,i] = hm_log_m3[i,j]
    }
  }
}

### extract tau t-statistics from raw models ###
for (i in 1:nrow(empty_matrix)) {
  index = 0.5 * (-i^2 + 31*i - 28)
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      lm <- convert_tbl(raw_model3[[index]])
      t_val <- lm[3,4]
      hm_raw_m3_tau[i, j] = t_val
   }
    if (i < j) {
      update_index = index + j - i
      hm_raw_m3_tau[i,j] = update_index
      lm <- convert_tbl(raw_model3[[update_index]])
      t_val <- lm[3,4]
      hm_raw_m3_tau[i,j] = t_val
      hm_raw_m3_tau[j,i] = hm_raw_m3_tau[i,j]
    }
  }
}

### extract tau t-statistics from log models ###
for (i in 1:nrow(empty_matrix)) {
  index = 0.5 * (-i^2 + 31*i - 28)
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      lm <- convert_tbl(log_model3[[index]])
      t_val <- lm[3,4]
      hm_log_m3_tau[i, j] = t_val
   }
    if (i < j) {
      update_index = index + j - i
      hm_log_m3_tau[i,j] = update_index
      lm <- convert_tbl(log_model3[[update_index]])
      t_val <- lm[3,4]
      hm_log_m3_tau[i,j] = t_val
      hm_log_m3_tau[j,i] = hm_log_m3_tau[i,j]
    }
  }
}
```

#model 4: heatmap of continuous interaction
```{r}
### raw values ###
raw_model4 <- sapply(dep.vars, run_model4, simplify = FALSE)
rm4_summaries <- lapply(raw_model4, summary)
rm4_summaries$NA_x_NA #sanity check

### log values ###
log_model4 <- sapply(dep.vars, run_logmodel4, simplify = FALSE)
lm4_summaries <- lapply(log_model4, summary)
lm4_summaries$DMN_x_DMN #sanity check

# POPULATE HEATMAP MATRICES #
hm_raw_m4 <- make_hm()
hm_log_m4 <- make_hm()

### extract centiloid*tau interaction t-statistic from raw models ###
for (i in 1:nrow(empty_matrix)) {
  index = 0.5 * (-i^2 + 31*i - 28)
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      lm <- convert_tbl(raw_model4[[index]])
      t_val <- lm[2,4]
      hm_raw_m4[i, j] = t_val
   }
    if (i < j) {
      update_index = index + j - i
      hm_raw_m4[i,j] = update_index
      lm <- convert_tbl(raw_model4[[update_index]])
      t_val <- lm[2,4]
      hm_raw_m4[i,j] = t_val
      hm_raw_m4[j,i] = hm_raw_m4[i,j]
    }
  }
}

### extract centiloid*tau interaction t-statistic from log models ###
for (i in 1:nrow(empty_matrix)) {
  index = 0.5 * (-i^2 + 31*i - 28)
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      lm <- convert_tbl(log_model4[[index]])
      t_val <- lm[2,4]
      hm_log_m4[i, j] = t_val
   }
    if (i < j) {
      update_index = index + j - i
      hm_log_m4[i,j] = update_index
      lm <- convert_tbl(log_model4[[update_index]])
      t_val <- lm[2,4]
      hm_log_m4[i,j] = t_val
      hm_log_m4[j,i] = hm_log_m4[i,j]
    }
  }
}
```

#model 5: heatmap of binarized interaction

```{r}
### raw values ###
raw_model5 <- sapply(dep.vars, run_model5, simplify = FALSE)
rm5_summaries <- lapply(raw_model5, summary)
rm5_summaries$NA_x_NA #sanity check

### log values ###
log_model5 <- sapply(dep.vars, run_logmodel5, simplify = FALSE)
lm5_summaries <- lapply(log_model5, summary)
lm5_summaries$DMN_x_DMN #sanity check

# POPULATE HEATMAP MATRICES #
hm_raw_m5 <- make_hm()
hm_log_m5 <- make_hm()

### extract centiloid(category)*tau interaction t-statistic from raw models ###
for (i in 1:nrow(empty_matrix)) {
  index = 0.5 * (-i^2 + 31*i - 28)
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      lm <- convert_tbl(raw_model5[[index]])
      t_val <- lm[2,4]
      hm_raw_m5[i, j] = t_val
   }
    if (i < j) {
      update_index = index + j - i
      hm_raw_m5[i,j] = update_index
      lm <- convert_tbl(raw_model5[[update_index]])
      t_val <- lm[2,4]
      hm_raw_m5[i,j] = t_val
      hm_raw_m5[j,i] = hm_raw_m5[i,j]
    }
  }
}

### extract centiloid(category)*tau interaction t-statistic from log models ###
for (i in 1:nrow(empty_matrix)) {
  index = 0.5 * (-i^2 + 31*i - 28)
  for (j in 1:ncol(empty_matrix)){
    if (i == j) {
      lm <- convert_tbl(log_model5[[index]])
      t_val <- lm[2,4]
      hm_log_m5[i, j] = t_val
   }
    if (i < j) {
      update_index = index + j - i
      hm_log_m5[i,j] = update_index
      lm <- convert_tbl(log_model5[[update_index]])
      t_val <- lm[2,4]
      hm_log_m5[i,j] = t_val
      hm_log_m5[j,i] = hm_log_m5[i,j]
    }
  }
}
```


#all models: create csv files
```{r}
# Write csv files #
write.csv(hm_raw_m3,file.path(out_path, "m3_raw_centiloid.csv"), row.names = TRUE)
write.csv(hm_log_m3,file.path(out_path, "m3_log_centiloid.csv"), row.names = TRUE)
write.csv(hm_raw_m3_tau,file.path(out_path, "m3_raw_tau.csv"), row.names = TRUE)
write.csv(hm_log_m3_tau,file.path(out_path, "m3_log_tau.csv"), row.names = TRUE)

write.csv(hm_raw_m4,file.path(out_path, "m4_raw.csv"), row.names = TRUE)
write.csv(hm_log_m4,file.path(out_path, "m4_log.csv"), row.names = TRUE)

write.csv(hm_raw_m5,file.path(out_path, "m5_raw.csv"), row.names = TRUE)
write.csv(hm_log_m5,file.path(out_path, "m5_log.csv"), row.names = TRUE)
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
